---
title: "complaints-project"
author: "steph gemmell"
date: "3/28/2021"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(htmlwidgets)
library(htmltools)
library(readr)

```

import data and analyze


```{r}

saveRDS(complaints, "complaints.rds")

complaints
View(complaints)

```

column lists whether consumers received a timely response or not - how often is the response not timely?

+ which "products" most frequently fall into this category?

```{r}

complaints %>% 
  count(timely_response == "No")

(3806/393050)*100

#slightly less than 1 percent of complaints did not receive a timely response
#when people did not get a timely response the products most frequently involved were:

not_timely <- complaints %>% 
  filter(timely_response == "No")

not_timely_freq <- complaints %>% 
  count(product)

not_timely_freq
glimpse(not_timely_freq)


```

the top five products involved when consumers did not receive a timely response were:

Credit reporting, credit repair services, or other personal consumer reports
255748

Debt collection
46088

Credit card or prepaid card
29128

Mortgage
20940

Checking or savings account
20679


what results did the consumers get on these complaints?

```{r}

not_timely %>% 
  count(company_response_to_consumer)

```

most frequently, the complaints were "closed with explanation"


```{r}




```











