---
title: "complaints-project"
author: "steph gemmell"
date: "3/28/2021"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(htmlwidgets)
library(htmltools)
library(readr)

```

import data and analyze

```{r}

saveRDS(complaints, "complaints.rds")

complaints
View(complaints)

```

column lists whether consumers received a timely response or not - how often is the response not timely?

+ which "products" most frequently fall into this category?

```{r}

complaints %>% 
  count(timely_response == "No")

(3806/393050)*100

#slightly less than 1 percent of complaints did not receive a timely response
#when people did not get a timely response the products most frequently involved were:

not_timely <- complaints %>% 
  filter(timely_response == "No")

not_timely_freq <- complaints %>% 
  count(product) %>% arrange(desc(n))

not_timely_freq
glimpse(not_timely_freq)


```

~~~~~the top five products involved when consumers did not receive a timely response were:~~~~~

Credit reporting, credit repair services, or other personal consumer reports
255748

Debt collection
46088

Credit card or prepaid card
29128

Mortgage
20940

Checking or savings account
20679


~~~~~what results did the consumers get on these complaints?~~~~~

```{r}

untimely_response <- not_timely %>% 
  count(company_response_to_consumer) %>%  arrange(desc(n))

untimely_response

```

most frequently, the complaints were "closed with explanation"

~~~~~what companies were involved most often?~~~~~


```{r}

complaint_cos <- not_timely %>% 
  count(company) %>% arrange(desc(n))

complaint_cos


```

~~~~~the top 10 companies involved with complaints that lacked a timely response were:~~~~~

Xerox State & Local Solutions, Inc.	
413			

Army and Air Force Exchange Service	
85		

Lending Club Corp	
84			

Atlanticus Services Corporation	
68		

MoneyLion Inc.	
64			

Carter-Young, Inc.	
61			

WAKEFIELD & ASSOCIATES, INC.	
56		

WELLS FARGO & COMPANY	
54			

AmerAssist A/R Solutions, Inc.	
52		

Capital Accounts, LLC	
51	

```{r}
#all datasets for flexdashboard

saveRDS(complaints, "complaints.rds")

not_timely <- complaints %>% 
  filter(timely_response == "No")

not_timely_freq <- complaints %>% 
  count(product)

complaint_cos <- not_timely %>% 
  count(company) %>% arrange(desc(n))

untimely_response <- not_timely %>% 
  count(company_response_to_consumer) %>%  arrange(desc(n))

```